### 2022-10-12 AISTATS2023/paper.tex
Updates from Overleaf

In this Section~\ref{sec:UALE-definition-1}, we define UALE. Then, we
provide an interval-based formulation that partitions the feature
domain into non-overlapping intervals (bin-splitting) and defines the
bin-effect and the bin-uncertainty
(Section~\ref{sec:UALE-definition-2}). Then, we present the UALE
approximation (Section~\ref{sec:UALE-approximation}), formally proving
the bin-splitting requirements for an unbiased estimation of the
uncertainty. Based on this, we present an optimization method to
determine an appropriate variable-width partitioning
(Section~\ref{sec:bin-spliting}).

>>>>

In Section~\ref{sec:UALE-definition-1} we define UALE and we
provide an interval-based formulation that partitions the feature
domain into non-overlapping intervals (bin-splitting) and defines the
bin-effect and the bin-uncertainty. Then, we present UALE
approximation (Section~\ref{sec:UALE-approximation}), formally proving
the bin-splitting requirements for an unbiased estimation of the
uncertainty. Based on this, we present an optimization method to
determine an appropriate variable-width partitioning
(Section~\ref{sec:bin-spliting}).
